Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-11-19 cbm-rbd-paper.tex
multicycle simulation
third simulation

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
For a numerical example, these relations are depicted in Figure~\ref{fig:tauhistfig2}.

@@

The horizon span $t_h$ can be determined by practical considerations,
but generally should reach far enough into the tail of $\Rsysnow(t)$
such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
Note that from \eqref{eq:gtnowtau} it is clear that one needs only ****

>>>>

Minimizing $\gnow(\tau)$ leads to $\tausnow$,
the optimal moment of maintenance on a prospective time scale.
The prospective unit cost rate $\cstarnow = \gnow(\tausnow)$ corresponding to $\tausnow$
thus is the lowest unit cost rate attainable for the span of the remaining lifetime of the system,
i.e., for what happens beyond current time $\tnow$.
Also of interest is the total cost rate at $\tnow$, denoted by $\ctotalnow$.
This gives the expected unit cost rate calculated over the full time since system start-up,
under the assumption that maintenance is scheduled for $\tstarnow = \tnow + \tausnow$.
$\ctotalnow$ generally decreases with $\tnow$ since for larger $\tnow$, maintenance costs are spread over a longer time.
However, when many (or few but critical) components fail, $\ctotalnow$ may increase,
since then, system failure becomes much more likely, leading to a higher $\cstarnow$.
These relations are depicted in Figure~\ref{fig:tauhistfig2}. %for a numerical example,

@@

The horizon span $t_h$ can be determined by practical considerations,
but generally should reach far enough into the tail of $\Rsysnow(t)$
such that $\gnow(\tau)$ is not cut off before it reaches its minimum. %one can be sure to find $\tausnow$.
Note that \eqref{eq:gtnowtau} indicates that values for $\Rsysnow(t)$ and $\fsysnow(t)$ 
only for $t \leq \tau$ are needed to calculate $\gnow(\tau)$.

We use \textsf{R} \citep{R} for our calculations,
using the package \texttt{ReliabilityTheory} \citep{2016:aslett-RT}
to calculate survival signatures.
As the parameter update step is closed-form,
$\tausnow$
